SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-07-26 scipy-1.0/covlett.tex
MAINT: revise cover letter
* revise cover letter based on reviewer
feedback in PR 193

% to adjust vertical spacing properties of
% newlfm class see: https://tex.stackexchange.com/a/65533/43006
%\unprtop{0mm}
\topmarginsize{0mm}
\topmarginskip{0in}
\headermarginsize{0in}
\headermarginskip{0in}
\MinHead{0in}
%\dateskipafter{0pt}
%\dateskipbefore{0pt}
%\sigskipbefore{0pt}
%\sigskipafter{0pt}
\closeskipbefore{1pt}
%\closeskipafter{0pt}
%\addrfromskipbefore{0pt}
\addrfromskipafter{0in}
\addrtoskipbefore{0in}
%\addrtoskipafter{0pt}
\newlfmP{Headlinewd=0pt,Footlinewd=0pt}
\newlfmP{sigsize=10pt}
\bottommarginskip{0pt}
\MinFoot{0pt}

\usepackage{kpfonts}
\usepackage{url}

\widowpenalty=1000
\clubpenalty=1000

@@

We have specifically chosen \emph{Nature Methods} because
SciPy lies at the base of the entire ecosystem of scientific methods
described in the journal scope, and because SciPy is effectively an
ever-improving methodological library. High-profile manuscripts citing SciPy 
extend beyond the biosciences to recent reports on gravitational waves and
black holes. Lacking a better alternative, these citations all point
to the SciPy website; instead, we think the package now merits a
formal publication in a highly visible journal. A pre-print will likely
soon be made available on arXiv.

@@

Thank you for your consideration.  We look forward to
    hearing from you.\vspace*{0.1cm}
\end{newlfm}
\end{document}

>>>>

% to adjust vertical spacing properties of
% newlfm class see: https://tex.stackexchange.com/a/65533/43006
%\unprtop{0mm}
\topmarginsize{0mm}
\topmarginskip{0in}
\headermarginsize{0in}
\headermarginskip{0in}
\MinHead{0in}
%\dateskipafter{0pt}
%\dateskipbefore{0pt}
\sigskipbefore{40pt}
%\sigskipafter{0pt}
\closeskipbefore{1pt}
%\closeskipafter{0pt}
%\addrfromskipbefore{0pt}
\addrfromskipafter{0in}
\addrtoskipbefore{0in}
%\addrtoskipafter{0pt}
\newlfmP{Headlinewd=0pt,Footlinewd=0pt}
\newlfmP{sigsize=10pt}
\bottommarginskip{60pt}
\MinFoot{0pt}

\usepackage{kpfonts}
\usepackage{hyperref}
\usepackage{url}

\hypersetup{%
  linkbordercolor=blue,% hyperlink borders will be blue
  pdfborderstyle={/S/U/W 1}% border style will be underline of width 1pt
}
\widowpenalty=1000
\clubpenalty=1000

@@

We have specifically chosen \emph{Nature Methods} because
SciPy lies at the base of the entire ecosystem of scientific methods
described in the journal scope, and because SciPy is effectively an
ever-improving methodological library. Among the 3000+ articles that 
cite the SciPy library are hundreds in the field of biology,
including several in \emph{Nature Methods}\footnote{\href{
https://www.nature.com/articles/s41592-018-0114-z}{
Gruber \emph{et al.} (2018) \textbf{15}: 832-836}
\href{https://www.nature.com/articles/s41592-019-0403-1}{
; Moen \emph{et al.} (2019)}}, one of which\footnote{
\href{https://www.nature.com/articles/nmeth.f.303}{
Caporaso \emph{et al.} (2010) \textbf{7}: 335-336}} is cited
15,800 times. Citations in recent reports on gravitational waves and
black holes are also striking. Lacking a better alternative, these citations all point
to the SciPy website; instead, we think the package now merits a
formal publication in a highly visible journal. A preprint was recently
made \href{https://arxiv.org/abs/1907.10121}{available on arXiv}.

@@

\vspace*{1cm}
Thank you for your consideration.  We look forward to
    hearing from you.
\end{newlfm}
\end{document}
